We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-04-17 paper/paper.tex
obs table updated

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
    \hline
    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}}
    & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} &
    \multicolumn{2}{c|}{\textbf{Normalized Units}}\\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-7}
    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
    %\hhline{~--}
    \hline
    Plane width (kpc) & $59\pm 3$  & $21\pm 2$  & $65\pm 12$   &
    $45\pm 8$    & $-0.48\pm 0.24$ & $-2.48\pm 0.26$\\\hline
    $c/a$ ratio & $0.45\pm 0.04$ & $0.25\pm 0.05$ & $0.55\pm0.10$ &
    $0.53\pm 0.10$ & $-1.03\pm 0.37$ & $-2.18\pm 0.42$\\ \hline
    $b/a$ ratio & $0.82\pm 0.06$ & $0.80\pm 0.04$ & $0.82\pm0.07$ &
    $0.81\pm 0.08$ & $-0.02\pm 0.82$ & $-0.13\pm 0.47$\\ \hline
  \end{tabular}
  \caption{Results from observations. Mean values and standard deviations for the different
    quantities describing the satellite distributions: plane width, $c/a$
    ratio and $b/a$ ratio. 
    The first column refers to the results from
    observational data, the second column uses the spherically
    randomized version of the observational data, the third column
    corresponds to the observational data recentered and normalized
    by the randomized values. \label{table:observations}}
\end{table*}

>>>>

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
    \hline
    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}}
    & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} &
    \multicolumn{2}{c|}{\textbf{Normalized Units}}\\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-7}
    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
    %\hhline{~--}
    \hline
Plane width (kpc) & $63.64$ & $19.34$ & $55.78$ & $38.60$ & $0.74$ & $-4.45$\\\hline
$c/a$ ratio & $0.42$ & $0.18$ & $0.51$ & $0.45$ & $-0.87$ & $-2.75$\\\hline
$b/a$ ratio & $0.96$ & $0.87$ & $0.82$ & $0.83$ & $1.74$ & $0.67$\\\hline
  \end{tabular}
  \caption{Results from observations with $N_s=11$. 
    for the different
    quantities describing the satellite distributions: plane width, $c/a$
    ratio and $b/a$ ratio. 
    The first column refers to the results from
    observational data, the second column uses the spherically
    randomized version of the observational data, the third column
    corresponds to the observational data recentered and normalized
    by the standard deviation of the randomized data. \label{table:observations}}
\end{table*}
